Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2018-02-19 paper.tex
Update on Overleaf.

We now describe the datasets and method used in our
evaluation~\footnote{Experimental data, additional figures and
source code can be downloaded from:
\url{http://github.com/digitisingscotland/pakdd2018-metric-linkage}.}.
We used three datasets from two
domains in our experiments, as summarised in Table~\ref{table-datasets}.
The first is \emph{Cora}~\cite{Cora2017}, which contains 1,295 records
that refer to 112 machine learning publications. Cora is commonly used
as a benchmark dataset in the literature for assessing linkage
algorithms. Ground truth is provided via a unique \emph{paper\_id}
identifier of the form ``blum1993". In this experiment linkage is
performed over the same set of records (i.e.\ a
de-duplication~\cite{Chr12}).

@@

\begin{table}[t]
\caption{Linkage quality on Cora dataset with distance threshold $d= 70$.}
\label{comparison-of-results-cora}
\centering
\begin{footnotesize}
\begin{tabular}{lrrrr} \hline\noalign{\smallskip}
Linker~~~~~~~~~~ & ~~~Comparisons & ~~~~~Precision & ~~~~~~~~~~~Recall & ~~~~~~F-measure \\
\noalign{\smallskip} \hline \noalign{\smallskip}
Brute Force     & 1,677,025 & 0.84 & 0.57 & 0.68 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
M-tree          &   902,693 & 0.84 & 0.57 & 0.68 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
LSH-2-2         &   192,199 & 0.95 & 0.47 & 0.63 \\
LSH-5-2         &   342,849 & 0.91 & 0.55 & 0.69 \\
LSH-10-2        &   513,947 & 0.88 & 0.57 & 0.69 \\
LSH-2-5         &    14,329 & 0.99 & 0.28 & 0.43 \\
LSH-5-5         &    22,057 & 0.99 & 0.36 & 0.53 \\
LSH-10-5        &    26,167 & 0.98 & 0.40 & 0.57 \\
LSH-2-10        &     4,711 &    1 & 0.15 & 0.27 \\
LSH-5-10        &     6,501 &    1 & 0.19 & 0.32 \\
LSH-10-10       &    10,627 & 0.99 & 0.27 & 0.43 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
Block-year      &   115,893 & 0.99 & 0.35 & 0.51 \\
Block-authors   &    11,039 & 0.94 & 0.16 & 0.28 \\
Block-title     &    27,407 & 0.95 & 0.42 & 0.58 \\
Block-venue     &    36,647 & 0.85 & 0.29 & 0.44 \\
Block-location  & 1,009,957 & 0.83 & 0.43 & 0.57 \\
Block-publisher &   833,079 & 0.85 & 0.44 & 0.58 \\
Block-combined  & 1,214,269 & 0.84 & 0.56 & 0.67 \\
\noalign{\smallskip} \hline
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.46\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-skye-mtree}
\vspace{-6mm}
\caption{M-tree linkage on Isle of Skye \\ dataset\label{skye-quality-mtree}}
\end{subfigure}%
~~
\begin{subfigure}{.46\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-kilmarnock-mtree}
\vspace{-6mm}
\caption{M-tree linkage on Kilmarnock \\ dataset \label{kilmarnock-quality-mtree}}
\end{subfigure} \vspace{1mm}

\begin{subfigure}{.46\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-skye-f}
\vspace{-6mm}
\caption{F-measure on Isle of Skye dataset \\ with M-tree and all
LSH configurations}
\end{subfigure}%
~~
\begin{subfigure}{.46\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-kilmarnock-f}
\vspace{-6mm}
\caption{F-measure on Kilmarnock dataset \\ with M-tree and all LSH configurations}
\end{subfigure}
\caption{Linkage results on the demographic datasets.}
\label{demography-quality}
\end{figure}

>>>>

We now describe the datasets and method used in our
evaluation~\footnote{Experimental data, additional figures and source
code can be downloaded from: \\
\url{http://github.com/digitisingscotland/pakdd2018-metric-linkage}.}.
We used three datasets from two domains in our experiments, as
summarised in Table~\ref{table-datasets}. The first is
\emph{Cora}~\cite{Cora2017}, which contains 1,295 records that refer to
112 machine learning publications. Cora is commonly used as a benchmark
dataset in the literature for assessing linkage algorithms. Ground truth
is provided via a unique \emph{paper\_id} identifier of the form
``blum1993". In this experiment linkage is performed over the same set
of records (i.e.\ a de-duplication~\cite{Chr12}).

@@

\begin{table}[t]
\caption{Linkage quality on Cora dataset with distance threshold $d= 70$.}
\label{comparison-of-results-cora}
\centering
\begin{footnotesize}
\begin{tabular}{lrrrr} \hline\noalign{\smallskip}
Linker~~~~~~~~~~ & ~~~Comparisons & ~~~~~Precision & ~~~~~~~~~~~Recall & ~~~~~~F-measure \\
\noalign{\smallskip} \hline \noalign{\smallskip}
Brute Force     & 1,677,025 & 0.84 & 0.57 & 0.68 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
M-tree          &   902,693 & 0.84 & 0.57 & 0.68 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
LSH-2-2         &   192,199 & 0.95 & 0.47 & 0.63 \\
LSH-5-2         &   342,849 & 0.91 & 0.55 & 0.69 \\
LSH-10-2        &   513,947 & 0.88 & 0.57 & 0.69 \\
LSH-2-5         &    14,329 & 0.99 & 0.28 & 0.43 \\
LSH-5-5         &    22,057 & 0.99 & 0.36 & 0.53 \\
LSH-10-5        &    26,167 & 0.98 & 0.40 & 0.57 \\
LSH-2-10        &     4,711 & 1.00 & 0.15 & 0.27 \\
LSH-5-10        &     6,501 & 1.00 & 0.19 & 0.32 \\
LSH-10-10       &    10,627 & 0.99 & 0.27 & 0.43 \\
\noalign{\smallskip} \hline \noalign{\smallskip}
Block-year      &   115,893 & 0.99 & 0.35 & 0.51 \\
Block-authors   &    11,039 & 0.94 & 0.16 & 0.28 \\
Block-title     &    27,407 & 0.95 & 0.42 & 0.58 \\
Block-venue     &    36,647 & 0.85 & 0.29 & 0.44 \\
Block-location  & 1,009,957 & 0.83 & 0.43 & 0.57 \\
Block-publisher &   833,079 & 0.85 & 0.44 & 0.58 \\
Block-combined  & 1,214,269 & 0.84 & 0.56 & 0.67 \\
\noalign{\smallskip} \hline
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-skye-mtree}
\vspace{-6mm}
\caption{M-tree on Isle of Skye dataset\label{skye-quality-mtree}}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-kilmarnock-mtree}
\vspace{-6mm}
\caption{M-tree on Kilmarnock dataset \label{kilmarnock-quality-mtree}}
\end{subfigure} \vspace{5mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-skye-f}
\vspace{-6mm}
\caption{F-measure on Isle of Skye dataset \\ with M-tree and all
LSH configurations}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-kilmarnock-f}
\vspace{-6mm}
\caption{F-measure on Kilmarnock dataset \\ with M-tree and all LSH configurations}
\end{subfigure}
\caption{Linkage results on the demographic datasets.}
\label{demography-quality}
\end{figure}
